### 2019-09-20 bp_results_1.tex
updates

\subsection{Explaining Stress Fluctuations}
We created a linear mixed model to attempt to explain some of the
stress that our participants were experiencing. We experimented with
multiple independent variables, including those derived from computer
interaction data such as total time spent actively on the computer,
percentage of time idle, and amount of time spent on non work-related
web browsing. We also looked at the day of the week and proximity to
beginning or end of month as possible explanatory variables. However,
ultimately we were unable to find any variable which showed a
significant correlation with our participants perceived stress
levels. This points to the need for additional instrumentation if we
are to succesfully understand and predict stress in the workplace.

>>>>

\subsection{Explaining Stress Fluctuations}
We created a linear mixed model with participants as random effects
to attempt to explain some of the
stress that our participants were experiencing. We experimented with day of the week and proximity to
beginning or end of month as possible explanatory variables. We also calculated
features from the gathered computer interaction data where available - namely total time spent actively on the computer,
percentage of time idle, and amount of time spent on non work-related
web browsing. However,
ultimately we were unable to find any variable which had
significant (p < 0.05) explanatory power with respect to our participants perceived stress
levels. This points to the need for additional instrumentation if we
are to succesfully understand and predict stress in the workplace.

### 2019-09-20 bp_studyMethod.tex
updates

In the second month of the study, we offered participants two Tai Chi classes per week (each in the middle of the day) in addition to the daily experience sampling and asked them to attend one class a week. We chose to offer Tai Chi class for two reasons: first, to incentivise participants for their continued participation and for keeping them engaged; and second, for their said benefits of reducing stress based on our consultation with researchers in psychiatry, psychology and more specifically on mindfulness practices.

@@

>>>>

In the second month of the study, we offered participants two one-hour Tai Chi classes per week (each in the middle of the day) in addition to the daily experience sampling and asked them to attend one class a week. We chose to offer Tai Chi class for two reasons: first, to incentivise participants for their continued participation and for keeping them engaged; and second, for their said benefits of reducing stress based on our consultation with researchers in psychiatry, psychology and more specifically on mindfulness practices.

@@

\subsubsection{Computer Interaction Data}
To gain a better understanding of our participants day-to-day work activities, we installed an open source computer interaction monitor (reference omitted for doubleblind.) to track the participant's active window, as well as keyboard and mouse activity. 4 of our participants opted out of this part of the study for privacy reasons (S6, S10, S12, and S13) so for this reason we did not include this data in our predictive model. However we did look at the computer interaction data as a potential part of an explanatory model.
